\ttitle

### 2016-03-25 Chapters/Pre_Post_SIRS.tex
Discussion update

%Aerobic capacity/comorbidity
Although CRP on POD 0 was significantly different between patients with a normal $\dot{V}_{O_2}$AT/$\dot{V}_{O_2}$Peak and those with low aerobic capacity, this difference was not present on other days. 
The lack of association between aerobic capacity, POSSUM Physiology Score and postoperative CRP in this study may have been due to the dominant effect of preoperative systemic inflammation and obstructive jaundice on the postoperative inflammatory response.
However, the association of postoperative hypoalbuminemia with low aerobic capacity, POSSUM Physiology Score and anaemia appears to suggest a link between comorbidity and systemic inflammation and/or nutritional status.
Bernal and co-workers studied 399 patients undergoing liver transplantation who had cardiopulmonary exercise testing as part of their preoperative work-up and reported that hypoalbuminemia was associated with both low $\dot{V}_{O_2}$AT and low $\dot{V}_{O_2}$Peak \parencite{bernal_aerobic_2014}.

%Body Composition
The association between hypoalbuminemia and low aerobic capacity may be explained by lower skeletal muscle and greater subcutaneous fat in patients with persistent postoperative hypoalbuminemia.
Richards and co-workers reported that elevated preoperative systemic inflammation was related to low skeletal muscle index \parencite{richards_relationships_2012}.
Hassen and co-workers reported that fat-free mass and skeletal muscle were inversely related to the severity of the postoperative inflammatory response following endo-vascular surgery for abdominal aortic aneurysm \parencite{hassen_preoperative_2007}.

Elevated systemic inflammation is related to obesity as well as sarcopenia. 
`Sarcopenic-obesity' in patients with pancreatic cancer where there is relative loss of skeletal muscle with preservation of adipose tissue puts these patients at particular risk for immune dysfunction \parencite{berg_adipose_2005, reisinger_sarcopenia_2015}, post-pancreatectomy complications \parencite{joglekar_sarcopenia_2015} and shorter long-term survival \parencite{tan_sarcopenia_2009, peng_impact_2012}.

>>>>

%Aerobic capacity/comorbidity
Although CRP on POD 0 was significantly different between patients with a normal $\dot{V}_{O_2}$AT/$\dot{V}_{O_2}$Peak and those with low aerobic capacity, this difference was not present on other days. 
The lack of association between aerobic capacity, POSSUM Physiology Score and postoperative CRP in this study may have been due to the dominant effect of preoperative systemic inflammation and obstructive jaundice on the postoperative inflammatory response.

%Body Composition

Richards and co-workers reported that elevated preoperative systemic inflammation was related to low skeletal muscle index \parencite{richards_relationships_2012}.
Hassen and co-workers reported that fat-free mass and skeletal muscle were inversely related to the severity of the postoperative inflammatory response following endo-vascular surgery for abdominal aortic aneurysm \parencite{hassen_preoperative_2007}.
Elevated systemic inflammation has been reported to be related to obesity as well as sarcopenia. 
`Sarcopenic-obesity' in patients with pancreatic cancer where there is relative loss of skeletal muscle with preservation of adipose tissue puts these patients at particular risk for immune dysfunction \parencite{berg_adipose_2005, reisinger_sarcopenia_2015}, post-pancreatectomy complications \parencite{joglekar_sarcopenia_2015} and shorter long-term survival \parencite{tan_sarcopenia_2009, peng_impact_2012}.
However, the present study did not identify any relationship between body composition and postoperative CRP levels.
This may have been due to several reasons including the effect of preoperative obstructive jaundice, hypoalbuminemia as well as cancer related inflammation and body composition changes.
